### 2021-02-09 final_report/include/backmatter/Appendix_2.tex
linked to new repo

\chapter{Installing, using and configuring the CA module} \label{b}
This appendix provides installation and usage instructions for the CA software developed as part of this thesis project, whose source code, as well as this report, is available at \url{https://github.com/aarneranta/concept-alignment}.

@@

\section{Configuration: modifying the alignment criteria}
As mentioned in Section \ref{criteria}, modifying the alignment criteria the program makes use of requires little effort. 
All criteria are in fact defined in a separate Haskell module \texttt{Criteria}\footnote{\url{https://github.com/aarneranta/concept-alignment/blob/master/Criteria.hs}} that exports only the list of criteria to be used. 
In the current implementation, it looks like this: \smallskip

>>>>

\chapter{Installing, using and configuring the CA module} \label{b}
This appendix provides installation and usage instructions for the CA software developed as part of this thesis project, whose source code, as well as this report, is available at \url{github.com/harisont/concept-alignment}.

@@

\section{Configuration: modifying the alignment criteria}
As mentioned in Section \ref{criteria}, modifying the alignment criteria the program makes use of requires little effort. 
All criteria are in fact defined in a separate Haskell module \texttt{Criteria}\footnote{\url{https://github.com/harisont/concept-alignment/blob/master/Criteria.hs}} that exports only the list of criteria to be used. 
In the current implementation, it looks like this: \smallskip
